Blueprint for efficient nuclear spin characterization with color center

### 2024-06-03 PRB - revision reply/main_revision.tex
resubmitted

%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle
%\tableofcontents
\section{Introduction and background}
Optically active defects in solids, known as color centers, have been utilized in various quantum applications \cite{awschalom2018quantum}, including quantum networks \cite{pompili2021realization}, quantum sensing \cite{degen2017quantum, meinel2023high}, and quantum registers \cite{bradley2019ten, vorobyov2021quantum, hesselmeier2023measuring, hesselmeier2024high, reiner2024high}.

@@

However, characterizing the hyperfine coupling of nuclear spins can be both challenging and time-consuming \cite{abobeih2019atomic, van2023mapping}. 
Traditionally, nuclear spin characterization is accomplished through Optically Detected Magnetic Resonance (ODMR) \cite{Dreau:2012aa,hesselmeier2023measuring}, but the spectroscopic resolution is constrained by the $1/T_2^\ast$ of the electron spin. 

@@

In particular, we consider the following common examples of nuclear spin registers that are ubiquitous in applications. First, the NV-like case with $S=1$ and weakly coupled nuclear spins, operating at high magnetic fields where $\gamma_n B \gg A_{zx}$ which has been extensively studied \cite{abobeih2019atomic, taminiau2012detection, Zhao:2014aa}.

@@

While double resonance methods \cite{Bradley:2019aa,zaiser2016enhancing} hold large promise for nuclear spin spectroscopy, they require additional experimental hardware, and often are not available. 

@@

\section{Hamiltonian}
\label{app:Hamiltonian}
The spin Hamiltonian for many color centers can be written as \cite{schweiger2001principles}:
\begin{gather}
	H = \mathbf{D}^\intercal \mathbf{S} \mathbf{D} + \beta_e \mathbf{B}^\intercal \mathbf{g} \mathbf{S} + \beta_n \sum_{k=1}^m g_n^{(k)}  \mathbf{B}^\intercal \mathbf{I}^{(k)} \notag \\
	+ \sum_{I_k>1/2} (\mathbf{I}^{\intercal} \mathbf{P} \mathbf{I})^{(k)} + \sum_{k=1}^m g_n^{(k)} (\mathbf{S}^\intercal \mathbf{A} \mathbf{I})^{(k)}
\end{gather}
Where $\mathbf{S}$ and $\mathbf{I}^{(k)}$ are electron and nuclear spin vector operators, $\mathbf{D}$ is zero field splitting tensor, $\mathbf{B}$ is magnetic field vector, $\mathbf{P}$ is nuclear quadrupole tensor, $\mathbf{A}$ is the hyperfine interaction tensor, $\beta_e = \frac{e \hbar}{2m_e}$ and $\beta_n = \frac{-e \hbar}{2m_n}$ are electron and nuclear Bohr magneton. Here, we neglected  nuclear-nuclear interactions. Also, due to axial symmetry, the zero field splitting can be simplified. We assume the magnetic field is only along the symmetry axis, which we denote as z direction. Moreover, the secular terms ($S_zI_x, S_zI_y, S_zI_z$) are just a shift of the energy level that are relevant up to first order, while the non-secular terms ($S_xI_x, S_yI_x, S_zI_z, S_xI_y, S_yI_y, S_zI_y$) mix the electron spin levels, which are largely detuned due to the large zero field splitting. Hence, the non-secular terms of Hamiltonian are neglected. Furthermore, for each nuclear spin, one can go to the xy frame such that $A_{zy}$ term is zero. All in all, the spin Hamiltonian with mentioned considerations can be simplified to:
\begin{gather}
	H = D_z S_z^2 + \gamma_e B S_z + \gamma_n B I_z^{(k)} + P_z^{(k)} I_z^{2(k)} \notag \\
	+ A_{zz}^{(k)} S_z I_z^{(k)} + A_{zx}^{(k)} S_z I_x^{(k)}
\end{gather}
The summation over k is omitted due to convenience!
The coefficient $\gamma_e$ and $\gamma_n$ are electron and nuclear gyromagnetic ratios. The coefficients' values for the case of NV center in diamond are $D_z= 2.87$ GHz, $\gamma_e= -2.802$ MHz/G, $\gamma_n^{(^{13}C)}= 1.07$ kHz/G, $\gamma_n^{(^{14}N)}= 0.31$ kHz/G, $P_z^{(^{14}N)}= -5.04$ MHz. \\

@@

The blind spot term, B, shows that how this sequence can be engineered to increase or reduce the signal amplitude of one nuclear spin from the spectrum. \st{The bright and blind spots of a frequency in the spectrum are as follows} \textcolor{black}{The Eq. \ref{eq:BS} suggests the bright and blind spots of a frequency can be obtained as follows}:
\begin{align}
	\text{Blind Spots:	} \tau = even \,\, \frac{\pi}{\omega}\\
	\text{Bright Spots:	} \tau = odd \,\, \frac{\pi}{\omega}
\end{align}
%\st{The blind spots does not depend only on one frequency but on the nuclear spin. It means if one resonant frequency is blinded, the other resonant frequency and all the multiple quantum resonances also vanishes. This can be used as a manifestation that which two peaks are from one nuclei. Also, This is very helpful especially in the presence of strongly coupled nuclear spin that suppress other nuclei. By sweeping $\tau_1$ and $\tau_2$, one can go through different bright and blind spots of each nuclear spin, observe which two peaks are correlated.}

@@

\section{DD analysis for bispecies systems}
\label{app:bispecies}
Consider a single color center that is surrounded by two nuclear spin species. Each species has a distinct bath, which is processing with its corresponding Larmor frequency. Assuming large Larmor frequency with respect to hyperfine couplings, one can write Eq. \ref{eq:approx_DD} for two bath ($\omega_0 \approx \omega_1 \approx \omega_L$) as follows:
	\expval{\sigma_z}_{bath} \approx 1 -2 k_1^2 \sin^4(\frac{\omega_L^{(1)} \tau}{2}) -2 k_2^2 \sin^4(\frac{\omega_L^{(2)} \tau}{2})
This means that two baths interfere, and the periodicity of the total bath is not straightforward any more. Hence, if there is a narrow peak next in DD signal, it can be attributed to both of the baths. To clarify the type of nuclear spins, one has to perform further experiments, e.g., in various external magnetic fields.
%pass
%\bibliography{references}% Produces the bibliography via BibTeX.
\begin{thebibliography}{24}%
\makeatletter
\providecommand \@ifxundefined [1]{%
 \@ifx{#1\undefined}
}%
\providecommand \@ifnum [1]{%
 \ifnum #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \@ifx [1]{%
 \ifx #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \natexlab [1]{#1}%
\providecommand \enquote  [1]{``#1''}%
\providecommand \bibnamefont  [1]{#1}%
\providecommand \bibfnamefont [1]{#1}%
\providecommand \citenamefont [1]{#1}%
\providecommand \href@noop [0]{\@secondoftwo}%
\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
\providecommand \@href[1]{\@@startlink{#1}\@@href}%
\providecommand \@@href[1]{\endgroup#1\@@endlink}%
\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
\providecommand \@@startlink[1]{}%
\providecommand \@@endlink[0]{}%
\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
\providecommand \urlprefix  [0]{URL }%
\providecommand \Eprint [0]{\href }%
\providecommand \doibase [0]{https://doi.org/}%
\providecommand \selectlanguage [0]{\@gobble}%
\providecommand \bibinfo  [0]{\@secondoftwo}%
\providecommand \bibfield  [0]{\@secondoftwo}%
\providecommand \translation [1]{[#1]}%
\providecommand \BibitemOpen [0]{}%
\providecommand \bibitemStop [0]{}%
\providecommand \bibitemNoStop [0]{.\EOS\space}%
\providecommand \EOS [0]{\spacefactor3000\relax}%
\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
\let\auto@bib@innerbib\@empty
%</preamble>
\bibitem [{\citenamefont {Awschalom}\ \emph {et~al.}(2018)\citenamefont
  {Awschalom}, \citenamefont {Hanson}, \citenamefont {Wrachtrup},\ and\
  \citenamefont {Zhou}}]{awschalom2018quantum}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~D.}\ \bibnamefont
  {Awschalom}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Hanson}},
  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Wrachtrup}},\ and\
  \bibinfo {author} {\bibfnamefont {B.~B.}\ \bibnamefont {Zhou}},\ }\bibfield
  {title} {\bibinfo {title} {Quantum technologies with optically interfaced
  solid-state spins},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
  {journal} {Nature Photonics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
  {pages} {516} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Pompili}\ \emph {et~al.}(2021)\citenamefont
  {Pompili}, \citenamefont {Hermans}, \citenamefont {Baier}, \citenamefont
  {Beukers}, \citenamefont {Humphreys}, \citenamefont {Schouten}, \citenamefont
  {Vermeulen}, \citenamefont {Tiggelman}, \citenamefont {dos Santos~Martins},
  \citenamefont {Dirkse} \emph {et~al.}}]{pompili2021realization}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Pompili}}, \bibinfo {author} {\bibfnamefont {S.~L.}\ \bibnamefont
  {Hermans}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Baier}},
  \bibinfo {author} {\bibfnamefont {H.~K.}\ \bibnamefont {Beukers}}, \bibinfo
  {author} {\bibfnamefont {P.~C.}\ \bibnamefont {Humphreys}}, \bibinfo {author}
  {\bibfnamefont {R.~N.}\ \bibnamefont {Schouten}}, \bibinfo {author}
  {\bibfnamefont {R.~F.}\ \bibnamefont {Vermeulen}}, \bibinfo {author}
  {\bibfnamefont {M.~J.}\ \bibnamefont {Tiggelman}}, \bibinfo {author}
  {\bibfnamefont {L.}~\bibnamefont {dos Santos~Martins}}, \bibinfo {author}
  {\bibfnamefont {B.}~\bibnamefont {Dirkse}}, \emph {et~al.},\ }\bibfield
  {title} {\bibinfo {title} {Realization of a multinode quantum network of
  remote solid-state qubits},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
  {journal} {Science}\ }\textbf {\bibinfo {volume} {372}},\ \bibinfo {pages}
  {259} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Degen}\ \emph {et~al.}(2017)\citenamefont {Degen},
  \citenamefont {Reinhard},\ and\ \citenamefont
  {Cappellaro}}]{degen2017quantum}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont
  {Degen}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Reinhard}},\
  and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Cappellaro}},\
  }\bibfield  {title} {\bibinfo {title} {Quantum sensing},\ }\href@noop {}
  {\bibfield  {journal} {\bibinfo  {journal} {Reviews of modern physics}\
  }\textbf {\bibinfo {volume} {89}},\ \bibinfo {pages} {035002} (\bibinfo
  {year} {2017})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Meinel}\ \emph {et~al.}(2023)\citenamefont {Meinel},
  \citenamefont {Kwon}, \citenamefont {Maier}, \citenamefont {Dasari},
  \citenamefont {Sumiya}, \citenamefont {Onoda}, \citenamefont {Isoya},
  \citenamefont {Vorobyov},\ and\ \citenamefont {Wrachtrup}}]{meinel2023high}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {Meinel}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Kwon}},
  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Maier}}, \bibinfo
  {author} {\bibfnamefont {D.}~\bibnamefont {Dasari}}, \bibinfo {author}
  {\bibfnamefont {H.}~\bibnamefont {Sumiya}}, \bibinfo {author} {\bibfnamefont
  {S.}~\bibnamefont {Onoda}}, \bibinfo {author} {\bibfnamefont
  {J.}~\bibnamefont {Isoya}}, \bibinfo {author} {\bibfnamefont
  {V.}~\bibnamefont {Vorobyov}},\ and\ \bibinfo {author} {\bibfnamefont
  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title}
  {High-resolution nanoscale nmr for arbitrary magnetic fields},\ }\href@noop
  {} {\bibfield  {journal} {\bibinfo  {journal} {Communications Physics}\
  }\textbf {\bibinfo {volume} {6}},\ \bibinfo {pages} {302} (\bibinfo {year}
  {2023})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Bradley}\ \emph {et~al.}(2019)\citenamefont
  {Bradley}, \citenamefont {Randall}, \citenamefont {Abobeih}, \citenamefont
  {Berrevoets}, \citenamefont {Degen}, \citenamefont {Bakker}, \citenamefont
  {Markham}, \citenamefont {Twitchen},\ and\ \citenamefont
  {Taminiau}}]{bradley2019ten}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~E.}\ \bibnamefont
  {Bradley}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Randall}},
  \bibinfo {author} {\bibfnamefont {M.~H.}\ \bibnamefont {Abobeih}}, \bibinfo
  {author} {\bibfnamefont {R.}~\bibnamefont {Berrevoets}}, \bibinfo {author}
  {\bibfnamefont {M.}~\bibnamefont {Degen}}, \bibinfo {author} {\bibfnamefont
  {M.~A.}\ \bibnamefont {Bakker}}, \bibinfo {author} {\bibfnamefont
  {M.}~\bibnamefont {Markham}}, \bibinfo {author} {\bibfnamefont
  {D.}~\bibnamefont {Twitchen}},\ and\ \bibinfo {author} {\bibfnamefont
  {T.~H.}\ \bibnamefont {Taminiau}},\ }\bibfield  {title} {\bibinfo {title} {A
  ten-qubit solid-state spin register with quantum memory up to one minute},\
  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
  X}\ }\textbf {\bibinfo {volume} {9}},\ \bibinfo {pages} {031045} (\bibinfo
  {year} {2019})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Vorobyov}\ \emph {et~al.}(2021)\citenamefont
  {Vorobyov}, \citenamefont {Zaiser}, \citenamefont {Abt}, \citenamefont
  {Meinel}, \citenamefont {Dasari}, \citenamefont {Neumann},\ and\
  \citenamefont {Wrachtrup}}]{vorobyov2021quantum}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
  {Vorobyov}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Zaiser}},
  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Abt}}, \bibinfo {author}
  {\bibfnamefont {J.}~\bibnamefont {Meinel}}, \bibinfo {author} {\bibfnamefont
  {D.}~\bibnamefont {Dasari}}, \bibinfo {author} {\bibfnamefont
  {P.}~\bibnamefont {Neumann}},\ and\ \bibinfo {author} {\bibfnamefont
  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title}
  {Quantum fourier transform for nanoscale quantum sensing},\ }\href@noop {}
  {\bibfield  {journal} {\bibinfo  {journal} {npj Quantum Information}\
  }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {124} (\bibinfo {year}
  {2021})}\BibitemShut {NoStop}%
  %7
\bibitem [{\citenamefont {Hesselmeier}\ \emph {et~al.}(2023)\citenamefont
  {Hesselmeier}, \citenamefont {Kuna}, \citenamefont {Tak{\'a}cs},
  \citenamefont {Iv{\'a}dy}, \citenamefont {Knolle}, \citenamefont {Ghezellou},
  \citenamefont {Ul-Hassan}, \citenamefont {Dasari}, \citenamefont {Kaiser},
  \citenamefont {Vorobyov} \emph {et~al.}}]{hesselmeier2023measuring}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont

>>>>

%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle
%\tableofcontents
\section{Introduction and background}
Optically active defects in solids, known as color centers, have been utilized in various quantum applications \cite{awschalom2018quantum}, including quantum networks \cite{pompili2021realization}, quantum sensing \cite{degen2017quantum, meinel2023high}, and quantum registers \cite{bradley2019ten, vorobyov2021quantum, hesselmeier2024qudit, hesselmeier2024high, reiner2024high}.

@@

However, characterizing the hyperfine coupling of nuclear spins can be both challenging and time-consuming \cite{abobeih2019atomic, van2024mapping}. 
Traditionally, nuclear spin characterization is accomplished through Optically Detected Magnetic Resonance (ODMR) \cite{dreau2012high,hesselmeier2024qudit}, but the spectroscopic resolution is constrained by the $1/T_2^\ast$ of the electron spin. 

@@

In particular, we consider the following common examples of nuclear spin registers that are ubiquitous in applications. First, the NV-like case with $S=1$ and weakly coupled nuclear spins, operating at high magnetic fields where $\gamma_n B \gg A_{zx}$ which has been extensively studied \cite{abobeih2019atomic, taminiau2012detection, zhao2014dynamical}.

@@

While double resonance methods \cite{bradley2019ten,zaiser2016enhancing} hold large promise for nuclear spin spectroscopy, they require additional experimental hardware, and often are not available. 

@@

\section{Hamiltonian}
\label{app:Hamiltonian}
The spin Hamiltonian for many color centers can be written as\cite{Schweiger2001Principles}:
\begin{gather}
	H = \mathbf{D}^\intercal \mathbf{S} \mathbf{D} + \beta_e \mathbf{B}^\intercal \mathbf{g} \mathbf{S} + \beta_n \sum_{k=1}^m g_n^{(k)}  \mathbf{B}^\intercal \mathbf{I}^{(k)} \notag \\
	+ \sum_{I_k>1/2} (\mathbf{I}^{\intercal} \mathbf{P} \mathbf{I})^{(k)} + \sum_{k=1}^m g_n^{(k)} (\mathbf{S}^\intercal \mathbf{A} \mathbf{I})^{(k)}
\end{gather}
Where $\mathbf{S}$ and $\mathbf{I}^{(k)}$ are electron and nuclear spin vector operators, $\mathbf{D}$ is zero field splitting tensor, $\mathbf{B}$ is magnetic field vector, $\mathbf{P}$ is nuclear quadrupole tensor, $\mathbf{A}$ is the hyperfine interaction tensor, $\beta_e = \frac{e \hbar}{2m_e}$ and $\beta_n = \frac{-e \hbar}{2m_n}$ are electron and nuclear Bohr magneton. Here, we neglected  nuclear-nuclear interactions. Also, due to axial symmetry, the zero field splitting can be simplified. We assume the magnetic field is only along the symmetry axis, which we denote as z direction. Moreover, the secular terms ($S_zI_x, S_zI_y, S_zI_z$) are just a shift of the energy level that are relevant up to first order, while the non-secular terms ($S_xI_x, S_yI_x, S_zI_z, S_xI_y, S_yI_y, S_zI_y$) mix the electron spin levels, which are largely detuned due to the large zero field splitting. Hence, the non-secular terms of Hamiltonian are neglected. Furthermore, for each nuclear spin, one can go to the xy frame such that $A_{zy}$ term is zero. All in all, the spin Hamiltonian with mentioned considerations can be simplified to:
\begin{gather}
	H = D_z S_z^2 + \gamma_e B S_z + \gamma_n B I_z^{(k)} + P_z^{(k)} I_z^{2(k)} \notag \\
	+ A_{zz}^{(k)} S_z I_z^{(k)} + A_{zx}^{(k)} S_z I_x^{(k)}
\end{gather}
The summation over k is omitted due to convenience!
The coefficient $\gamma_e$ and $\gamma_n$ are electron and nuclear gyromagnetic ratios. The coefficients' values for the case of NV center in diamond are $D_z= 2.87$ GHz, $\gamma_e= -2.802$ MHz/G, $\gamma_n^{(^{13}C)}= 1.07$ kHz/G, $\gamma_n^{(^{14}N)}= 0.31$ kHz/G, $P_z^{(^{14}N)}= -5.04$ MHz. \\

@@

The blind spot term, B, shows that how this sequence can be engineered to increase or reduce the signal amplitude of one nuclear spin from the spectrum. 
%\st{The bright and blind spots of a frequency in the spectrum are as follows} 
\textcolor{black}{The Eq. \ref{eq:BS} suggests the bright and blind spots of a frequency can be obtained as follows}:
\begin{align}
	\text{Blind Spots:	} \tau = even \,\, \frac{\pi}{\omega}\\
	\text{Bright Spots:	} \tau = odd \,\, \frac{\pi}{\omega}
\end{align}
%\st{The blind spots does not depend only on one frequency but on the nuclear spin. It means if one resonant frequency is blinded, the other resonant frequency and all the multiple quantum resonances also vanishes. This can be used as a manifestation that which two peaks are from one nuclei. Also, This is very helpful especially in the presence of strongly coupled nuclear spin that suppress other nuclei. By sweeping $\tau_1$ and $\tau_2$, one can go through different bright and blind spots of each nuclear spin, observe which two peaks are correlated.}

@@

\section{DD analysis for bispecies systems}
\label{app:bispecies}
Consider a single color center that is surrounded by two nuclear spin species. Each species has a distinct bath, which is processing with its corresponding Larmor frequency. Assuming large Larmor frequency with respect to hyperfine couplings, one can write Eq. \ref{eq:approx_DD} for two bath ($\omega_0 \approx \omega_1 \approx \omega_L$) as follows:
\begin{gather}
	\expval{\sigma_z}_{bath} \approx 1 -2 k_1^2 \sin^4(\frac{\omega_L^{(1)} \tau}{2}) -2 k_2^2 \sin^4(\frac{\omega_L^{(2)} \tau}{2})
\end{gather}
This means that two baths interfere, and the periodicity of the total bath is not straightforward any more. Hence, if there is a narrow peak next in DD signal, it can be attributed to both of the baths. To clarify the type of nuclear spins, one has to perform further experiments, e.g., in various external magnetic fields.
%pass
\bibliography{references_review}% Produces the bibliography via BibTeX.

%\begin{thebibliography}{24}%
%\makeatletter
%\providecommand \@ifxundefined [1]{%
% \@ifx{#1\undefined}
%}%
%\providecommand \@ifnum [1]{%
% \ifnum #1\expandafter \@firstoftwo
% \else \expandafter \@secondoftwo
% \fi
%}%
%\providecommand \@ifx [1]{%
% \ifx #1\expandafter \@firstoftwo
% \else \expandafter \@secondoftwo
% \fi
%}%
%\providecommand \natexlab [1]{#1}%
%\providecommand \enquote  [1]{``#1''}%
%\providecommand \bibnamefont  [1]{#1}%
%\providecommand \bibfnamefont [1]{#1}%
%\providecommand \citenamefont [1]{#1}%
%\providecommand \href@noop [0]{\@secondoftwo}%
%\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
%\providecommand \@href[1]{\@@startlink{#1}\@@href}%
%\providecommand \@@href[1]{\endgroup#1\@@endlink}%
%\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
%  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
%\providecommand \@@startlink[1]{}%
%\providecommand \@@endlink[0]{}%
%\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
%\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
%\providecommand \urlprefix  [0]{URL }%
%\providecommand \Eprint [0]{\href }%
%\providecommand \doibase [0]{https://doi.org/}%
%\providecommand \selectlanguage [0]{\@gobble}%
%\providecommand \bibinfo  [0]{\@secondoftwo}%
%\providecommand \bibfield  [0]{\@secondoftwo}%
%\providecommand \translation [1]{[#1]}%
%\providecommand \BibitemOpen [0]{}%
%\providecommand \bibitemStop [0]{}%
%\providecommand \bibitemNoStop [0]{.\EOS\space}%
%\providecommand \EOS [0]{\spacefactor3000\relax}%
%\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
%\let\auto@bib@innerbib\@empty
%%</preamble>
%\bibitem [{\citenamefont {Awschalom}\ \emph {et~al.}(2018)\citenamefont
%  {Awschalom}, \citenamefont {Hanson}, \citenamefont {Wrachtrup},\ and\
%  \citenamefont {Zhou}}]{awschalom2018quantum}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~D.}\ \bibnamefont
%  {Awschalom}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Hanson}},
%  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Wrachtrup}},\ and\
%  \bibinfo {author} {\bibfnamefont {B.~B.}\ \bibnamefont {Zhou}},\ }\bibfield
%  {title} {\bibinfo {title} {Quantum technologies with optically interfaced
%  solid-state spins},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
%  {journal} {Nature Photonics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
%  {pages} {516} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Pompili}\ \emph {et~al.}(2021)\citenamefont
%  {Pompili}, \citenamefont {Hermans}, \citenamefont {Baier}, \citenamefont
%  {Beukers}, \citenamefont {Humphreys}, \citenamefont {Schouten}, \citenamefont
%  {Vermeulen}, \citenamefont {Tiggelman}, \citenamefont {dos Santos~Martins},
%  \citenamefont {Dirkse} \emph {et~al.}}]{pompili2021realization}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
%  {Pompili}}, \bibinfo {author} {\bibfnamefont {S.~L.}\ \bibnamefont
%  {Hermans}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Baier}},
%  \bibinfo {author} {\bibfnamefont {H.~K.}\ \bibnamefont {Beukers}}, \bibinfo
%  {author} {\bibfnamefont {P.~C.}\ \bibnamefont {Humphreys}}, \bibinfo {author}
%  {\bibfnamefont {R.~N.}\ \bibnamefont {Schouten}}, \bibinfo {author}
%  {\bibfnamefont {R.~F.}\ \bibnamefont {Vermeulen}}, \bibinfo {author}
%  {\bibfnamefont {M.~J.}\ \bibnamefont {Tiggelman}}, \bibinfo {author}
%  {\bibfnamefont {L.}~\bibnamefont {dos Santos~Martins}}, \bibinfo {author}
%  {\bibfnamefont {B.}~\bibnamefont {Dirkse}}, \emph {et~al.},\ }\bibfield
%  {title} {\bibinfo {title} {Realization of a multinode quantum network of
%  remote solid-state qubits},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
%  {journal} {Science}\ }\textbf {\bibinfo {volume} {372}},\ \bibinfo {pages}
%  {259} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Degen}\ \emph {et~al.}(2017)\citenamefont {Degen},
%  \citenamefont {Reinhard},\ and\ \citenamefont
%  {Cappellaro}}]{degen2017quantum}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont
%  {Degen}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Reinhard}},\
%  and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Cappellaro}},\
%  }\bibfield  {title} {\bibinfo {title} {Quantum sensing},\ }\href@noop {}
%  {\bibfield  {journal} {\bibinfo  {journal} {Reviews of modern physics}\
%  }\textbf {\bibinfo {volume} {89}},\ \bibinfo {pages} {035002} (\bibinfo
%  {year} {2017})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Meinel}\ \emph {et~al.}(2023)\citenamefont {Meinel},
%  \citenamefont {Kwon}, \citenamefont {Maier}, \citenamefont {Dasari},
%  \citenamefont {Sumiya}, \citenamefont {Onoda}, \citenamefont {Isoya},
%  \citenamefont {Vorobyov},\ and\ \citenamefont {Wrachtrup}}]{meinel2023high}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
%  {Meinel}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Kwon}},
%  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Maier}}, \bibinfo
%  {author} {\bibfnamefont {D.}~\bibnamefont {Dasari}}, \bibinfo {author}
%  {\bibfnamefont {H.}~\bibnamefont {Sumiya}}, \bibinfo {author} {\bibfnamefont
%  {S.}~\bibnamefont {Onoda}}, \bibinfo {author} {\bibfnamefont
%  {J.}~\bibnamefont {Isoya}}, \bibinfo {author} {\bibfnamefont
%  {V.}~\bibnamefont {Vorobyov}},\ and\ \bibinfo {author} {\bibfnamefont
%  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title}
%  {High-resolution nanoscale nmr for arbitrary magnetic fields},\ }\href@noop
%  {} {\bibfield  {journal} {\bibinfo  {journal} {Communications Physics}\
%  }\textbf {\bibinfo {volume} {6}},\ \bibinfo {pages} {302} (\bibinfo {year}
%  {2023})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Bradley}\ \emph {et~al.}(2019)\citenamefont
%  {Bradley}, \citenamefont {Randall}, \citenamefont {Abobeih}, \citenamefont
%  {Berrevoets}, \citenamefont {Degen}, \citenamefont {Bakker}, \citenamefont
%  {Markham}, \citenamefont {Twitchen},\ and\ \citenamefont
%  {Taminiau}}]{bradley2019ten}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~E.}\ \bibnamefont
%  {Bradley}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Randall}},
%  \bibinfo {author} {\bibfnamefont {M.~H.}\ \bibnamefont {Abobeih}}, \bibinfo
%  {author} {\bibfnamefont {R.}~\bibnamefont {Berrevoets}}, \bibinfo {author}
%  {\bibfnamefont {M.}~\bibnamefont {Degen}}, \bibinfo {author} {\bibfnamefont
%  {M.~A.}\ \bibnamefont {Bakker}}, \bibinfo {author} {\bibfnamefont
%  {M.}~\bibnamefont {Markham}}, \bibinfo {author} {\bibfnamefont
%  {D.}~\bibnamefont {Twitchen}},\ and\ \bibinfo {author} {\bibfnamefont
%  {T.~H.}\ \bibnamefont {Taminiau}},\ }\bibfield  {title} {\bibinfo {title} {A
%  ten-qubit solid-state spin register with quantum memory up to one minute},\
%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
%  X}\ }\textbf {\bibinfo {volume} {9}},\ \bibinfo {pages} {031045} (\bibinfo
%  {year} {2019})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Vorobyov}\ \emph {et~al.}(2021)\citenamefont
%  {Vorobyov}, \citenamefont {Zaiser}, \citenamefont {Abt}, \citenamefont
%  {Meinel}, \citenamefont {Dasari}, \citenamefont {Neumann},\ and\
%  \citenamefont {Wrachtrup}}]{vorobyov2021quantum}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
%  {Vorobyov}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Zaiser}},
%  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Abt}}, \bibinfo {author}
%  {\bibfnamefont {J.}~\bibnamefont {Meinel}}, \bibinfo {author} {\bibfnamefont
%  {D.}~\bibnamefont {Dasari}}, \bibinfo {author} {\bibfnamefont
%  {P.}~\bibnamefont {Neumann}},\ and\ \bibinfo {author} {\bibfnamefont
%  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title}
%  {Quantum fourier transform for nanoscale quantum sensing},\ }\href@noop {}
%  {\bibfield  {journal} {\bibinfo  {journal} {npj Quantum Information}\
%  }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {124} (\bibinfo {year}
%  {2021})}\BibitemShut {NoStop}%
%  %7
%\bibitem [{\citenamefont {Hesselmeier}\ \emph {et~al.}(2023)\citenamefont
%  {Hesselmeier}, \citenamefont {Kuna}, \citenamefont {Tak{\'a}cs},
%  \citenamefont {Iv{\'a}dy}, \citenamefont {Knolle}, \citenamefont {Ghezellou},
%  \citenamefont {Ul-Hassan}, \citenamefont {Dasari}, \citenamefont {Kaiser},
